Hierarchy Builder

### 2020-04-27 coqws/easychair.tex
fix caption
fix Ring

\documentclass{easychair}
%\documentclass[EPiC]{easychair}
%\documentclass[EPiCempty]{easychair}
%\documentclass[debug]{easychair}
%\documentclass[verbose]{easychair}
%\documentclass[notimes]{easychair}
%\documentclass[withtimes]{easychair}
%\documentclass[a4paper]{easychair}
%\documentclass[letterpaper]{easychair}
\usepackage{wrapfig}

@@

\begin{wrapfigure}[0]{r}{.35\textwidth}
  \vspace{1em}
  \includegraphics[width=.35\textwidth]{diagram.pdf}
  \vspace{-1.5em}
  %\caption{
    \center{\small{Figure 1: The hierarchy}}
   % }
  \label{fig:hierarchy}
\end{wrapfigure}
\
\begin{coqcode}

@@

(* A statement in the signature of a Semiring S.  *)
Check forall S : SemiRing.type, forall x : S, x * 1 + 0 = x.

(* We need no additional mixin to declare the structure of rings. *)
HB.structure Definition SemiRing := { A of SemiRing_of_CMonoid A & AbelianGrp_of_CMonoid A & }.

@@

For space constraints we omit the declaration
of the green arrows in Figure 1 which are alternative interfaces
called factories. They provide specialized interfaces to
build structures for others.
Factories are used to accommodate the insertion of
intermediate structures in a hierarchy without breaking user code, as we all
as to implement shortcuts: the factory to build a \coq{Ring} from \coq{Type}
(rightmost green arrow)
can omit the commutativity axiom of the addition, since it is implied
by the other axioms~\cite{nearrings}.
\bibliography{biblio}

>>>>

\documentclass{easychair}
%\documentclass[EPiC]{easychair}
%\documentclass[EPiCempty]{easychair}
%\documentclass[debug]{easychair}
%\documentclass[verbose]{easychair}
%\documentclass[notimes]{easychair}
%\documentclass[withtimes]{easychair}
%\documentclass[a4paper]{easychair}
%\documentclass[letterpaper]{easychair}
\usepackage{wrapfig}
\usepackage[font=small,labelfont=bf]{caption}

@@

\begin{wrapfigure}[0]{r}{.35\textwidth}
  \vspace{1em}
  \includegraphics[width=.35\textwidth]{diagram.pdf}
  \vspace{-1.5em}
  \caption{The hierarchy}
  \label{fig:hierarchy}
\end{wrapfigure}
\
\begin{coqcode}

@@

(* A statement in the signature of a `SemiRing` S.  *)
Check forall S : SemiRing.type, forall x : S, x * 1 + 0 = x.

(* We need no additional mixin to declare the `Ring` structure. *)
HB.structure Definition Ring := { A of SemiRing_of_CMonoid A & AbelianGrp_of_CMonoid A & }.

@@

For space constraints we omit the declaration
of the green arrows in Fig.~\ref{fig:hierarchy} which are alternative interfaces
called factories. They provide specialized interfaces to
build structures for others.
Factories are used to accommodate the insertion of
intermediate structures in a hierarchy without breaking user code, as we all
as to implement shortcuts: the factory to build a \coq{Ring} from \coq{Type}
(rightmost green arrow)
can omit the commutativity axiom of the addition, since it is implied
by the other axioms~\cite{nearrings}.
\bibliography{biblio}
